Paper on the carbonate chemistry at Ny-Ålesund

### 2020-03-13 paper.Rmd
refined water masses chunk

```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
d_all <- as_tibble(
  #readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
  readRDS(file = paste0(path_data, "fb_data/d_all_copy.rds"))
) %>%
  filter(sal_fb > 28) # remove salinity data lower than 28
```

@@

```{r water masses, fig.width=15, fig.height=15, echo=FALSE, message= FALSE}
# One tries to identify water masses coming from the Atlantic or freshwater
temp_sal <- d_all %>%
  ggplot(aes(x = sal_fb, y = temp_insitu, col = month), na.rm=TRUE) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="Temperature vs salinity SBE45",x="Salinity", y="Temp. (°C)") +
  coord_fixed() +
  Mytheme(size_labs = 8) #+
  #theme(axis.text.x=element_blank())
#  +annotation_custom(grob_A)
print(temp_sal)

den <- seacarb::rho(S = d_all$sal_fb , T = d_all$temp_insitu, P = 1)
d_all <- d_all %>%
  dplyr::mutate(den = den)
ts_den <- d_all %>%
  ggplot(aes(x = datetime, y = den), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="Density",x="Time", y="Density") +
  #coord_fixed() +
  Mytheme(size_labs = 8)
print(ts_den)
```

>>>>

```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
d_all <- as_tibble(
  readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
  #readRDS(file = paste0(path_data, "fb_data/d_all_copy.rds"))
) %>%
  filter(sal_fb > 28) # remove salinity data lower than 28
```

@@

#Temperature vs salinity
We explore the use of a TS diagram to investigate changes in water sources. Now need to calculate slopes and r2, and see whether some months have a consistently different behaviour.

```{r temperature vs salinity, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
# One tries to identify water masses coming from the Atlantic or freshwater
den <- rho(S = s, T = t, P = 1)
s <- c(seq(30.4, 35.3, by=0.1)) # pCO2
t <- seq(-2, 8, by=0.1) #temperature throughout the year
grid <- as_tibble(expand.grid(s, t)) %>%
  rename(s=Var1, t=Var2) %>%
  mutate(z=rho(S = s, T = t, P = 1))

tmp <- ggplot(data = z, 
              aes(x=s, y=s, z = z), na.rm = TRUE) +
  geom_contour()

d <- d_all %>%
  dplyr::filter(year < 2020) %>%
  dplyr::mutate(month=month(datetime, label = TRUE, abbr = TRUE)) # abbreviated months rather than digital months
  #ggplot(aes(x = sal_fb, y = temp_insitu), na.rm=TRUE) +
temp_sal <-  ggplot() +
  geom_point(data = d, aes(x = sal_fb, y = temp_insitu, fill=month), na.rm=TRUE,
             size=size_point) + 
  labs(title="Temperature vs salinity SBE45", x="Salinity", y="Temp. (°C)") +
  facet_wrap(~ year, ncol = 5) +
  stat_smooth(data = d, aes(x = sal_fb, y = temp_insitu, color=month),
              method=lm, na.rm=TRUE, show.legend=TRUE, se=FALSE) +
  geom_contour(data = d, aes(x = s, y = t, z = z)) +
  coord_fixed() +
  Mytheme(size_labs = 14) +
  #scale_color_viridis(name="Month", discrete=TRUE, option="plasma")
print(temp_sal)
```

```{r density, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
d_all <- d_all %>%
  dplyr::mutate(den = den)
ts_den <- d_all %>%
  ggplot(aes(x = datetime, y = den), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="Density",x="Time", y="Density") +
  #coord_fixed() +
  Mytheme(size_labs = 14)
print(ts_den)
```
